Alex Popescu - Final Stats

### 2024-09-25 Data & Scripts/Alex Popescu - Final Stats.Rmd
Habituation test completed

# Bookkeeping

```{r Packages, include = F}
library("tidyverse")
library("psych")
library("car")
library("ggplot2")
library("lmerTest")
library("robustlmm")
library("sjPlot")
library("effects")
library("doBy")
library("emmeans")
library("formattable")
library("dplyr")
library("descr")
library("MASS")
library("jmv")
library("webshot")
library("kableExtra")
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
```

@@

>>>>

# Bookkeeping
```{r Packages, include = F}
library("tidyverse")
library("psych")
library("car")
library("ggplot2")
library("lmerTest")
library("robustlmm")
library("sjPlot")
library("effects")
library("doBy")
library("emmeans")
library("formattable")
library("dplyr")
library("descr")
library("MASS")
library("jmv")
library("webshot")
library("kableExtra")
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
```

@@

## Habituation
```{r plot habituation}
Habit<-BOUT.raw %>%
   filter(., BEHAVIOR == "HU", LATITUDE == "43.18262") %>%
           ggplot(.
               , aes(x = JULIAN_DATE
                     , y = DURATION
                     )) +
  geom_point() +
  geom_smooth(method="lm") +
  theme_classic() +
  xlab("Sampling Date") +
  ylab("Duration of bouts of alertness (s)") +
  theme(text = element_text(size = 18, family = "serif"))
Habit

```{r Habituation test - opportunistic sampling}
Habit.MOD.opp<-lm(DURATION~JULIAN_DATE, data = subset(BOUT.raw, BOUT.raw$BEHAVIOR == "HU" & BOUT.raw$LATITUDE != "43.18262" & BOUT.raw$BAIT_PRESENCE == "YES"))

sjPlot::tab_model(Habit.MOD.opp
                  , show.stat = T
                  , show.se = T
                  , digits = 4
                  , show.re.var = T
                  , title = ""
                  , dv.labels = ""
)
```

```{r Habituation test - recurrent sampling}
Habit.MOD.rec<-lm(DURATION~JULIAN_DATE, data = subset(BOUT.raw, BOUT.raw$BEHAVIOR == "HU" & BOUT.raw$LATITUDE == "43.18262" & BOUT.raw$BAIT_PRESENCE == "YES"))

sjPlot::tab_model(Habit.MOD.rec
                  , show.stat = T
                  , show.se = T
                  , digits = 4
                  , show.re.var = T
                  , title = ""
                  , dv.labels = ""
)
```
